---
title: "FamiliaR with Dynamics"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    social: menu
    source_code: embed
    theme: spacelab
runtime: shiny
---

<style>

.form-control {
    width: 90%;
    }

</style>


```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(datasets)
library(ggplot2)
library(bslib)
options(shiny.maxRequestSize = 30*1024^2)
data(faithful)
Solow1 <- function(s,k,a){
  y <- s*k^a
  return <- y
}
Solow2 <- function(d,k){
  y <- d*k+k^-1
}
solow_de <- function(t,y,parameters){
  s <- parameters[1]
  a <- parameters[2]
  del <- parameters[3]
  #k <- parameters[4]
  rhs <- s*y^a
  lhs <- del*y+(1/y)
  dy = rhs-lhs
  list(dy)
}
goodwin2<-function(t, state, parameters) {
  with(as.list(c(state, parameters)),{
    dV <- (a-b*U)*V
    dU <- (-c+d*V)*U
    dQ <- ((1-U)/sigma)*Q
    list(c(dV, dU, dQ))})}
goodwin <- function(t, y, parameters) {
  x <- y[1]
  y <- y[2]
  sigma <- parameters[1]
  alpha <- parameters[2]
  beta <- parameters[3]
  gamma <- parameters[4]
  rho <- parameters[5]
  A <- 1/sigma - alpha - beta
  B <- 1/sigma
  C <- gamma+alpha
  D <- rho
  dy <- numeric(2)
  dy[1] <- A*x - B*x*y
  dy[2] <- C*x*y - D*y
  list(dy)
}
```

Dynamics {data-navmenu='Models' data-icon='ion-levels'}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

Select your model and the value of each parameters.

```{r}
selectInput("model", label = "Economic Model:",
            choices = c("Solow", "Ramsey", "OLG", "Goodwin"), selected = "Solow")
conditionalPanel("input.model == 'Solow'",
                 sliderInput("k", label = "Chart length (k):", min = 1, max = 100, value = 20, step = 1),
                 sliderInput("s", label = "Saving rate:", min = 0, max = 1, value =0.2, step = 0.01),
                 sliderInput("a", label = "Elasticty:", min = 0, max = 1, value =0.3, step = 0.01),
                 sliderInput("d", label = "Depreciation:", min = 0, max = 1, value =0.02, step = 0.01),
                 sliderInput("n", label = "Population growth rate:", min = 0, max = 1, value =0.5, step = 0.01),
                 sliderInput("t", label = "Time", min = 0, max = 100, value =20, step = 5),
                 numericInput('k0', 'Initial capital, k0:', 3, min=0.5, max=200)
                 
)
conditionalPanel("input.model == 'Ramsey'",
                 sliderInput("t", label = "Time", min = 0, max = 200, value = 50, step = 5),
                 sliderInput("c", label = "Consumption, dc/dt",min = 0, max = 5, value = 3, step = 0.05),
                 sliderInput("k", label = "Capital, dk/dt", min = 0, max = 50, value = 30, step = 0.5),
                 sliderInput("theta", label = "Elasticity, tendendy of consumers to smooth their consumption over time:", min = 0, max = 1, value = 0.03, step = 0.01),
                 sliderInput("rho", label = "Rate at which consumers discount their future consumption", min = 0, max = 1, value = 0.2, step = 0.01),
                 sliderInput("delta", label = "Depreciation rate of capital", min = 0, max = 1, value = 0.1, step = 0.01),
                 sliderInput("alpha", label = "Elasticity parameter (measuring the responsiveness of the output production to changes in the input capital):", min = 0, max = 1, value = 0.3, step = 0.01),
                 
)    
```

Column
-----------------------------------------------------------------------


### Downloads per sec (last 5 min) {data-height=200}
```{r}
 
sliderInput("initial_values", label="initial values", min=1, max=5, value=1, step=1)
conditionalPanel("input.initial_values == 1",
                 numericInput('aa1', 'a', 1 ))
conditionalPanel("input.initial_values == 2",
                 fillRow(numericInput('aa2', 'a', 1),
                         numericInput('bb2', 'b', 1)))
conditionalPanel("input.initial_values == 3",
                 fillRow(numericInput('aa3', 'a', 1),
                         numericInput('bb3', 'b', 1),
                         numericInput('cc3', 'c', 1)))
conditionalPanel("input.initial_values == 4",
                 fillRow(
                   numericInput('aa4', 'a', 1),
                   numericInput('bb4', 'b', 1),
                   numericInput('cc4', 'c', 1),
                   numericInput('dd4', 'd', 1))
                 )
                 
conditionalPanel("input.initial_values == 5",
                 fillRow(
                   numericInput('aa5', 'a', 1),
                   numericInput('bb5', 'b', 1),
                   numericInput('cc5', 'c', 1),
                   numericInput('dd5', 'd', 1),
                   numericInput('ee5', 'e', 1))
                 )
actionButton("go","(Re)start Numeric Simulation", style="background-color: #ec7063 ; border-radius: 10px !important; border: none; position:absolute; bottom: 5px; margin: auto;"
)

```





### Numerical Simulations

```{r}
 initial_val <- eventReactive(input$go, {
   print(typeof(input$initial_values))
   nval <- input$initial_values
   print(paste("nval=",nval))
   if(nval==1){return(c(input$aa1))} 
   else if (nval==2){return(c(input$aa2,input$bb2))}
   else if(nval==3){return(c(input$aa3,input$bb3,input$cc3))}
   else if(nval==4){return(c(input$aa4,input$bb4,input$cc4,input$dd4))}
   else {return(c(input$aa5,input$bb5,input$cc5,input$dd5,input$ee5))}
 
   # ifelse(nval==1, c(a),
   #        ifelse(nval==2, c(a,b),
   #               ifelse(nval==3, c(a,b,c), 
   #                      ifelse(nval==4, c(a,b,c,d), 
   #                             c(a,b,c,d,e)))))
   })
 
 renderPlot({
   ini <- initial_val()
   if (input$model == "Solow")  {
     phaseR::flowField(solow_de,
               xlim   = c(0.0001, input$t),
               ylim   = c(0.0001, input$k),
               parameters = c(input$s,input$a,input$d),
               points=10,
               system = 'one.dim',
               add = F,
               xlab = 't',
               ylab = 'dk/dt')
     
     phaseR::nullclines(solow_de,
                       xlim   = c(0.0001, input$t),
                       ylim <- c(0.0001,input$k),
                       parameters = c(input$s,input$a,input$d),
                       system = "one.dim",
                       state.names = 'k')
     
     phaseR::trajectory(solow_de,
                   y0 = ini, 
                   tlim = c(0, input$t),
                   parameters = c(input$s,input$a,input$d), 
                   system = "one.dim", 
                   #colour = rep("black"),
                   add = T)
   }
   else if (input$model == "Goodwin")  {
     parameters <- c(a = 1.5,
                 b = 1.8,
                 c = 0.8,
                 d = 0.8,
                 sigma=0.8)
     state <- c(V = 0.5,
            U = 1,
            Q = 1)
     times <- seq(0, 20, by = 0.01)
     out <- deSolve::ode(y = state, times = times, func = goodwin2, parms = parameters)
     par(oma = c(0, 0, 3, 0))
     plot(out, xlab = "time", ylab = "-")
   }
   
   else if (input$model == "Ramsey"){
     ramsey.flowField <- phaseR::flowField(
     ramsey,
     xlim = c(0.01,input$k),
     ylim = c(0.01,input$c),
     parameters = c(0.2,0.03,0.1,0.3),
                  points = 10,
                  add=F
 )
     grid()
     
     ramsey.nullclines <- phaseR::nullclines(
     ramsey,
     xlim = c(0,input$k),
     ylim = c(0.01,input$c),
     state.names = c('k','c'),
     parameters = c(0.2,0.03,0.1,0.3),
     points = 500,
     col = c("blue","red"),
     add.legend=T
 )
     
   }
     
 })
```

Column {.tabset}
--------------------------------------------------------------------

### Dynamics

```{r}
#renderPrint(input$model)
#uiOutput("dynamic")
renderPlot({
  k <- 1:input$k
  if (input$model == "Solow")  {
    ggplot()+
      geom_line(aes(x = k, y = Solow1(input$s,k, input$a), color = "blue"))+
      geom_line(aes(x=k,y=Solow2(input$d, k), color = "red"))+
      theme_bw()
    #plot(k,Solow(input$s,k, input$a), type="l")
    #lines(k,Solow(input$s,k, -input$a), type="l")
    }
})
```

### Phase Portrait/Phase Diagram

```{r}
renderPlot({
  if (input$model == "Solow"){
    phaseR::phasePortrait(solow_de,
                      ylim <- c(0.5,input$k),
                      parameters = c(input$s,input$a,input$d),
                      col = 'black',
                      add.grid = T,
                      xlab='k',
                      ylab='dk/dt')
  }
  if (input$model == "Goodwin"){
    phaseR::flowField(goodwin, 
                                     xlim = c(0,1.5), 
                                     ylim = c(0, 1.5), 
                                     parameters = c(0.25, 0.6, 0.2, 0.3, 0.4), 
                                     points = 19, 
                                     add = FALSE)
    phaseR::nullclines(goodwin, 
                                       xlim = c(0,1.5), 
                                       ylim = c(0, 1.5),
                                       parameters = c(0.25, 0.6, 0.2, 0.3, 0.4), 
                                       points = 500)
  y0 <- matrix(c(0.2, 1, 0.6, 1, 1.1, 1), ncol = 2, nrow = 3, byrow = TRUE)
  phaseR::trajectory(goodwin, 
                                       y0 = y0, 
                                       tlim = c(0,10),
                                       parameters = c(0.25, 0.6, 0.2, 0.3, 0.4), 
                                       colour = rep("black", 3))
}
})
```



PhaseR and Our Tool{data-navmenu='About this Project' data-icon="ion-cube"} 
========================================================================

Link and short presentation of the package and the paper associated. 

Future Perspectives{data-navmenu='About this Project' data-icon='ion-ios-paperplane-outline'} 
========================================================================

Possibility of a package, extending/generalizing the tool to all macro 1-ODE and 2-ODE...

Resources{data-navmenu='Models' data-icon='ion-merge'}
========================================================================

In that page we can propose short econ/math developments on the models and/or links to the papers and teaching courses
