---
title: "FamiliaR with Dynamics"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    source_code: embed
    theme: spacelab
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(datasets)
library(ggplot2)
data(faithful)

Solow1 <- function(s,k,a){
  y <- s*k^a
  return <- y
}
Solow2 <- function(d,n,k){
  y <- d*k + n*k
}

solow_de <- function(t,y,parameters){
  s <- parameters[1]
  a <- parameters[2]
  del <- parameters[3]
  #k <- parameters[4]
  rhs <- s*y^a
  lhs <- del*y+(1/y)
  dy = rhs-lhs
  list(dy)
}
```

Dynamics {data-navmenu='Models' data-icon='ion-levels'}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

Select your model and the value of each parameters.

```{r}
selectInput("model", label = "Economic Model:",
            choices = c("Solow", "Ramset", "OLG"), selected = "Solow")
sliderInput("k", label = "Chart length (k):",
            min = 1, max = 100, value = 10, step = 1)
sliderInput("s", label = "Saving rate:",
            min = 0, max = 1, value =0.5, step = 0.01)
sliderInput("a", label = "Elasticty:",
            min = 0, max = 1, value =0.5, step = 0.01)
sliderInput("d", label = "Depreciation:",
            min = 0, max = 1, value =0.02, step = 0.01)
sliderInput("n", label = "Population growth rate:",
            min = 0, max = 1, value =0.5, step = 0.01)
sliderInput("t", label = "Time",
            min = 0, max = 300, value =50, step = 5)
```

Column
-----------------------------------------------------------------------

### Numerical Simulations

```{r}
renderPlot({
  if (input$model == "Solow")  {
    phaseR::flowField(solow_de,
              xlim   = c(0.0001, input$t),
              ylim   = c(0.0001, input$k),
              parameters = c(input$s,input$a,input$d),
              points=10,
              system = 'one.dim',
              add = F,
              xlab = 't',
              ylab = 'dk/dt')
    
    phaseR::nullclines(solow_de,
                      xlim   = c(0.0001, input$t),
                      ylim <- c(0.0001,input$k),
                      parameters = c(input$s,input$a,input$d),
                      system = "one.dim",
                      state.names = 'k')
    
    phaseR::trajectory(solow_de, 
                  y0 = c(2.5,4.35,10,20,23,27), 
                  tlim = c(0,500),
                  parameters = c(input$s,input$a,input$d), 
                  system = "one.dim", 
                  colour = rep("black"),
                  add = T)
    }
})

```


Column {.tabset}
-----------------------------------------------------------------------

### Dynamics

```{r}
#renderPrint(input$model)
#uiOutput("dynamic")
renderPlot({
  k <- 1:input$k
  if (input$model == "Solow")  {
    ggplot()+
      geom_line(aes(x = k, y = Solow1(input$s,k, input$a), color = "blue"))+
      geom_line(aes(x=k,y=Solow2(input$d, input$n, k), color = "red"))
    #plot(k,Solow(input$s,k, input$a), type="l")
    #lines(k,Solow(input$s,k, -input$a), type="l")
    }
})
```

### Phase Portrait

```{r}
renderPlot({
  if (input$model == "Solow"){
    phaseR::phasePortrait(solow_de,
                      ylim <- c(0.5,input$k),
                      parameters = c(input$s,input$a,input$d),
                      col = 'black',
                      add.grid = T,
                      xlab='k',
                      ylab='dk/dt')
  }
})

```



PhaseR and Our Tool{data-navmenu='About this Project' data-icon="ion-cube"} 
========================================================================

Link and short presentation of the package and the paper associated. 

Future Perspectives{data-navmenu='About this Project' data-icon='ion-ios-paperplane-outline'} 
========================================================================

Possibility of a package, extending/generalizing the tool to all macro 1-ODE and 2-ODE...

Resources{data-navmenu='Models' data-icon='ion-merge'}
========================================================================

In that page we can propose short econ/math developments on the models and/or links to the papers and teaching courses

