---
title: "FamiliaR with Dynamics"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    source_code: embed
    theme: spacelab
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(datasets)
library(ggplot2)
data(faithful)
Solow1 <- function(s,k,a){
  y <- s*k^a
  return <- y
}
Solow2 <- function(d,n,k){
  y <- d*k + n*k
}
```

Dynamics {data-navmenu='Models' data-icon='ion-levels'}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

Select your model and the value of each parameters.

```{r}
selectInput("model", label = "Economic Model:",
            choices = c("Solow", "Ramset", "OLG"), selected = "Solow")
sliderInput("k", label = "Chart length (k):",
            min = 1, max = 20, value = 10, step = 1)
sliderInput("s", label = "Saving rate:",
            min = 0, max = 1, value =0.5, step = 0.01)
sliderInput("a", label = "Elasticty:",
            min = 0, max = 1, value =0.5, step = 0.01)
sliderInput("d", label = "Depreciation:",
            min = 0, max = 1, value =0.5, step = 0.01)
sliderInput("n", label = "Population growth rate:",
            min = 0, max = 1, value =0.5, step = 0.01)
```

Column
-----------------------------------------------------------------------

### Numerical Simulations

Column {.tabset}
-----------------------------------------------------------------------

### Dynamics

```{r}
#renderPrint(input$model)
#uiOutput("dynamic")
renderPlot({
  k <- 1:input$k
  if (input$model == "Solow")  {
    ggplot()+
      geom_line(aes(x = k, y = Solow1(input$s,k, input$a), color = "blue"))+
      geom_line(aes(x=k,y=Solow2(input$d, input$n, k), color = "red"))
    #plot(k,Solow(input$s,k, input$a), type="l")
    #lines(k,Solow(input$s,k, -input$a), type="l")
    }
})
```

### Phase Portrait




PhaseR and Our Tool{data-navmenu='About this Project' data-icon="ion-cube"} 
========================================================================

Link and short presentation of the package and the paper associated. 

Future Perspectives{data-navmenu='About this Project' data-icon='ion-ios-paperplane-outline'} 
========================================================================

Possibility of a package, extending/generalizing the tool to all macro 1-ODE and 2-ODE...

Resources{data-navmenu='Models' data-icon='ion-merge'}
========================================================================

In that page we can propose short econ/math developments on the models and/or links to the papers and teaching courses
