#The following code is the yaml code that define the basic instruction for a flexdashboard project
---
title: "FamiliaR with Dynamics"
output: 
  flexdashboard::flex_dashboard:
    orientation: column
    social: menu
    source_code: embed
    theme: spacelab
runtime: shiny
---

#The following code is a css code that adjust the size of numerical simulation input sliders windows
<style>

.form-control {
    width: 90%;
    }

</style>


```{r global, include=FALSE}
#Required libraries for the project
library(datasets)
library(ggplot2)
library(bslib)
library(shinycssloaders)
options(shiny.maxRequestSize = 30*1024^2)
data(faithful)
#Dynamic functions used for the project
Solow1 <- function(s,k,a){
  y <- s*k^a
  return <- y
}
Solow2 <- function(d,k){
  y <- d*k+k^-1
}
solow_de <- function(t,y,parameters){
  s <- parameters[1]
  a <- parameters[2]
  del <- parameters[3]
  #k <- parameters[4]
  rhs <- s*y^a
  lhs <- del*y+(1/y)
  dy = rhs-lhs
  list(dy)
}
goodwin2<-function(t, state, parameters) {
  with(as.list(c(state, parameters)),{
    sigma <- parameters[1]
    alpha <- parameters[2]
    beta <- parameters[3]
    gamma <- parameters[4]
    rho <- parameters[5]
    A <- 1/sigma - alpha - beta
    B <- 1/sigma
    C <- gamma+alpha
    D <- rho
    dV <- (A-B*U)*V
    dU <- (-C+D*V)*U
    dQ <- ((1-U)/sigma)*Q
    list(c(dV, dU, dQ))})}
goodwin <- function(t, y, parameters) {
  x <- y[1]
  y <- y[2]
  sigma <- parameters[1]
  alpha <- parameters[2]
  beta <- parameters[3]
  gamma <- parameters[4]
  rho <- parameters[5]
  A <- 1/sigma - alpha - beta
  B <- 1/sigma
  C <- gamma+alpha
  D <- rho
  dy <- numeric(2)
  dy[1] <- A*x - B*x*y
  dy[2] <- -C*y +D*y*x
  list(dy)
}
ramsey <- function(t, y, parameters) {
  x <- y[1] #capital dc/dt
  y <- y[2] #consumption dk/dt
  theta <- parameters[1]
  rho <- parameters[2]
  delta <- parameters[3]
  alpha <- parameters[4]
  dy <- numeric(2)
  r <- alpha*x^(alpha-1)
  dy[1] <- x^alpha-y-delta*x
  dy[2] <- (y*(r-theta-delta))/delta
  list(dy)
}
shone <- function(t, y, parameters){
  ry <- y[1] # real output
  pie <- y[2] # expected inflation
  c0 <- parameters[1]
  i0 <- parameters[2]
  G <- parameters[3]
  b <- parameters[4]
  k <- parameters[5]
  d <- parameters[6]
  h <- parameters[7]
  tau <- parameters[8]
  alpha <- parameters[9]
  beta <- parameters[10]
  mdot <- parameters[11]
  yn <- parameters[12]
  a0 <- (c0+i0+G)/(1-b*(1-tau)+((h*k)/d))
  a1 <- (h/d)/(1-b*(1-tau)+((h*k)/d))
  a2 <- h/(1-b*(1-tau)+((h*k)/d))
  dy <- numeric(2)
  dy[1] <- a1*mdot-alpha*(a1-a2*beta)*(ry-yn)-a1*pie
  dy[2] <- beta*alpha*(y-yn)
  list(dy)
}
```

Dynamics {data-navmenu='Models' data-icon='ion-levels'}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

Select your model and the value of each parameters.

```{r}
#selectInpt object that asks the user which economic model has to be studied
selectInput("model", label = "Economic Model:",
            choices = c("Solow", "Ramsey", "OLG", "Goodwin"), selected = "Solow")
#set of conditional panels object which, depending on selectInput user choice, "reactively" display the respective parameter sliders. A sliderInput object creates a slider given some options
conditionalPanel("input.model == 'Solow'",
                 sliderInput("k", label = "Chart length (k):", min = 1, max = 100, value = 20, step = 1),
                 sliderInput("s", label = "Saving rate:", min = 0, max = 1, value =0.2, step = 0.01),
                 sliderInput("a", label = "Elasticty:", min = 0, max = 1, value =0.3, step = 0.01),
                 sliderInput("d", label = "Depreciation:", min = 0, max = 1, value =0.02, step = 0.01),
                 sliderInput("n", label = "Population growth rate:", min = 0, max = 1, value =0.5, step = 0.01),
                 sliderInput("t", label = "Time", min = 0, max = 100, value =20, step = 5)
)
conditionalPanel("input.model == 'Ramsey'",
                 sliderInput("tr", label = "Time", min = 0, max = 200, value = 50, step = 5),
                 sliderInput("cr", label = "Consumption, dc/dt",min = 0, max = 5, value = 3, step = 0.05),
                 sliderInput("kr", label = "Capital, dk/dt", min = 0, max = 50, value = 30, step = 0.5),
                 sliderInput("thetar", label = "Elasticity, tendendy of consumers to smooth their consumption over time:", min = 0, max = 1, value = 0.03, step = 0.01),
                 sliderInput("rhor", label = "Rate at which consumers discount their future consumption", min = 0, max = 1, value = 0.2, step = 0.01),
                 sliderInput("deltar", label = "Depreciation rate of capital", min = 0, max = 1, value = 0.1, step = 0.01),
                 sliderInput("alphar", label = "Elasticity parameter (measuring the responsiveness of the output production to changes in the input capital):", min = 0, max = 1, value = 0.3, step = 0.01),
                 
)
conditionalPanel("input.model == 'Goodwin'",
                 sliderInput("alphag", label = "Technical progress growth rate", min = 0, max = 1, value = 0.0196, step = 0.0001),
                 sliderInput("betag", label = "Labour force growth rate",min = 0, max = 1, value = 0.016, step = 0.0001),
                 sliderInput("gammag", label = "Real Phillips curve intercept", min = 0, max = 1, value = 0.13, step = 0.0001),
                 sliderInput("rhog", label = "Real Phillips curve slope", min = 0, max = 1, value = 0.96, step = 0.0001),
                 sliderInput("sigmag", label = "Capital-output ratio", min = 0, max = 5, value = 3, step = 0.0001),
                 sliderInput("tg", label = "Time", min=1, max=1000, value=130, step=1)
                 )
```

Column
-----------------------------------------------------------------------


### Initial values {data-height=350}
```{r}
 #the following code display, depending on a sliderInput choice, the initial conditions for all the available model. It is important that each shiny object take a univoque name otherwise errors will occur. This is the reason for very strange names (e.g gaa1), sorry Pier Giuseppe for our lack of fantasy ;)
 ####################################################
#Conditional panel for initial values for Solow model#
 ####################################################
conditionalPanel("input.model == 'Solow'",
sliderInput("initial_values", label="initial values", min=1, max=5, value=1, step=1),
conditionalPanel("input.initial_values == 1",
                 numericInput('aa1', 'a', 1 )),
conditionalPanel("input.initial_values == 2",
                 fillRow(numericInput('aa2', 'a', 1),
                         numericInput('bb2', 'b', 1))),
conditionalPanel("input.initial_values == 3",
                 fillRow(numericInput('aa3', 'a', 1),
                         numericInput('bb3', 'b', 1),
                         numericInput('cc3', 'c', 1))),
conditionalPanel("input.initial_values == 4",
                 fillRow(
                   numericInput('aa4', 'a', 1),
                   numericInput('bb4', 'b', 1),
                   numericInput('cc4', 'c', 1),
                   numericInput('dd4', 'd', 1))
                 ),
                 
conditionalPanel("input.initial_values == 5",
                 fillRow(
                   numericInput('aa5', 'a', 1),
                   numericInput('bb5', 'b', 1),
                   numericInput('cc5', 'c', 1),
                   numericInput('dd5', 'd', 1),
                   numericInput('ee5', 'e', 1))
                 ),
actionButton("go_sol","(Re)start Numeric Simulation Solow", style="background-color: #ec7063 ; border-radius: 10px !important; border: none; position:absolute; bottom: 5px; margin: auto;"
))

 ######################################################
#Conditional panel for initial values for Goodwin model#
 #####################################################
#y0 <- matrix(c(0.2, 1, 0.6, 1, 1.1, 1), ncol = 2, nrow = 3, byrow = TRUE)
conditionalPanel("input.model == 'Goodwin'",
                 fluidPage(
                   fluidRow(
                     sliderInput("initial_values_g",
                                 label="initial values",
                                 min=1,
                                 max=3,
                                 value=1,
                                 step=1)
                     ),
                   fluidRow(
                     conditionalPanel("input.initial_values_g == 1",
                                      numericInput('gaa1', 'a', 0.2 ),
                                      numericInput('gbb1', 'b', 1)),
                     conditionalPanel("input.initial_values_g == 2",
                                      column(6,
                                             numericInput('gaa2', 'a1', 0.2),
                                             numericInput('gbb2', 'b1', 1)),
                                      column(6,
                                             numericInput('gcc2', 'a2',0.6),
                                             numericInput('gdd2', 'b2',1))),
                     conditionalPanel("input.initial_values_g == 3",
                                      column(4,
                                             numericInput('gaa3', 'a1', 0.2),
                                             numericInput('gbb3', 'b1', 1)),
                                      column(4,
                                             numericInput('gcc3', 'a2', 0.6),
                                             numericInput('gdd3', 'b2', 1)),
                                      column(4,
                                             numericInput('gee3', 'a3', 0.8),
                                             numericInput('gff3', 'b3', 1)))),
                   fluidRow(
                     actionButton("go_good",
                                  "(Re)start Numeric Simulation", 
                                  style="background-color: #ec7063 ; border-radius: 10px !important; border: none; position:absolute; bottom: 5px; margin: auto;"))))


 ######################################################
#Conditional panel for initial values for Ramsey model#
 #####################################################


 conditionalPanel("input.model == 'Ramsey'",
                  fluidPage(
                    fluidRow(
                      sliderInput("initial_values_r",
                                  label="initial values",
                                  min=1,
                                  max=3,
                                  value=1,
                                  step=1)
                      ),
                    fluidRow(
                      conditionalPanel("input.initial_values_r == 1",
                                       numericInput('raa1', 'a', 0.2 ),
                                       numericInput('rbb1', 'b', 1)),
                      conditionalPanel("input.initial_values_r == 2",
                                       column(6,
                                              numericInput('raa2', 'a1', 0.2),
                                              numericInput('rbb2', 'b1', 1)),
                                       column(6,
                                              numericInput('rcc2', 'a2',0.6),
                                              numericInput('rdd2', 'b2',1))),
                      conditionalPanel("input.initial_values_r == 3",
                                       column(4,
                                              numericInput('raa3', 'a1', 0.2),
                                              numericInput('rbb3', 'b1', 1)),
                                       column(4,
                                              numericInput('rcc3', 'a2', 0.6),
                                              numericInput('rdd3', 'b2', 1)),
                                       column(4,
                                              numericInput('ree3', 'a3', 0.8),
                                              numericInput('rff3', 'b3', 1)))),
                    fluidRow(
                      actionButton("go_ram",
                                   "(Re)start Numeric Simulation", 
                                   style="background-color: #ec7063 ; border-radius: 10px !important; border: none; position:absolute; bottom: 5px; margin: auto;"))))

```





### Numerical Simulations


```{r}
#this is one of the trickiest part of our code, we want the plot to update every time the initial values are modified AND the go button is pressed. To do so we define the initial_val function that uses the eventReactive function. This function update the initial_val every time the go button is pressed.
At the same time, the renderPlot function is waiting for any update inside the curly brackets. Once the go button is pressed the plot is rendered.
  initial_val <- eventReactive(input$go_sol, {
      print(input$initial_values)
   print(typeof(input$initial_values))
   nval <- input$initial_values
   print(paste("nval=",nval))
   if(nval==1){return(c(input$aa1))} 
   else if (nval==2){return(c(input$aa2,input$bb2))}
   else if(nval==3){return(c(input$aa3,input$bb3,input$cc3))}
   else if(nval==4){return(c(input$aa4,input$bb4,input$cc4,input$dd4))}
   else {return(c(input$aa5,input$bb5,input$cc5,input$dd5,input$ee5))}})
   
initial_val_g <- eventReactive(input$go_good, {
  return(c(input$gaa2,input$gbb2))})
 
conditionalPanel("input.model == 'Solow'",
                 absolutePanel(
                        width = "100%", height = "100%",
                 renderPlot({
                   ini <- initial_val()
                   phaseR::flowField(solow_de,
                                     xlim   = c(0.0001, input$t),
                                     ylim   = c(0.0001, input$k),
                                     parameters = c(input$s,input$a,input$d),
                                     points=10,
                                     system = 'one.dim',
                                     add = F,
                                     xlab = 't',
                                     ylab = 'dk/dt') #flowfield are generated trhough phaseR, as nullclines and trajectories.
                   phaseR::nullclines(solow_de,
                                      xlim   = c(0.0001, input$t),
                                      ylim <- c(0.0001,input$k),
                                      parameters = c(input$s,input$a,input$d),
                                      system = "one.dim",
                                      state.names = 'k')
                   phaseR::trajectory(solow_de,
                                      y0 = ini,
                                      tlim = c(0, input$t),
                                      parameters = c(input$s,input$a,input$d),
                                      system = "one.dim",
                                      add = T)})))


conditionalPanel("input.model == 'Goodwin'",
                 absolutePanel(
                        width = "100%", height = "100%",
                 renderPlot({
                   ini_g <- y_in()
                   parameters <-  c(input$sigmag, input$alphag, input$betag, input$gammag, input$rhog)
                   state <- c(V = ini_g[1,1], #0.5
                              U = ini_g[2,1], #1
                              Q = 1)
                   times <- seq(0, input$tg, by = 0.01)
                   out <- deSolve::ode(y = state, times = times, func = goodwin2, parms = parameters)
                   par(oma = c(0, 0, 3, 0))
                   plot(out, xlab = "time", ylab = "-")})))

conditionalPanel("input.model == 'Ramsey'",
                 absolutePanel(
                        width = "100%", height = "100%",
                        ((
                 renderPlot({
                   ramsey.numericalSolution <- phaseR::numericalSolution(
                     ramsey,
                     y0 = c(0.5,0.1),
                     tlim = c(0,input$tr),
                     tstep = 0.01,
                     add.grid = T,
                     type = "one",
                     parameters = c(input$thetar,input$rhor,input$deltar,input$alphar),
                     ylab = "x,y",
                     xlab = "t",
                     ylim = c(0,5))})))))
```

Column {.tabset}
--------------------------------------------------------------------

### Dynamics

```{r}
#the following code gave annoyng issues about graphical representation. The problems were solved trough absolutePanel() and specific width and height commands.
fluidPage(
conditionalPanel("input.model == 'Solow'",
                 absolutePanel(
                        width = "100%", height = "100%",
                        renderPlot({
                          k <- 1:input$k
                          ggplot()+
                            geom_line(aes(x = k, y = Solow1(input$s,k, input$a), color = "blue"))+
                            geom_line(aes(x=k,y=Solow2(input$d, k), color = "red"))+
                            theme_bw()
    #plot(k,Solow(input$s,k, input$a), type="l")
    #lines(k,Solow(input$s,k, -input$a), type="l")
    }))))
```

### Phase Portrait/Phase Diagram

```{r}
y_in <- eventReactive(input$go_good, {
  if(input$initial_values_g==1){
    return(matrix(c(input$gaa1, input$gbb1), ncol = 1, nrow = 2, byrow = TRUE))}
  else if(input$initial_values_g==2){
      return(matrix(c(input$gaa2, input$gbb2, input$gcc2, input$gdd2), ncol = 2, nrow = 2, byrow = TRUE))}
  else{return(matrix(c(input$gaa3, input$gbb3, input$gcc3, input$gdd3, input$gee3, input$gff3), ncol = 3, nrow = 2, byrow = TRUE))}})

conditionalPanel("input.model == 'Solow'",
                 absolutePanel(
                        width = "100%", height = "100%",
                 renderPlot({
                   phaseR::phasePortrait(solow_de,
                                         ylim <- c(0.5,input$k),
                                         parameters = c(input$s,input$a,input$d),
                                         col = 'black',
                                         add.grid = T,
                                         xlab='k',
                                         ylab='dk/dt')})))

conditionalPanel("input.model == 'Goodwin'",
                 absolutePanel(
                        width = "100%", height = "100%",
                 renderPlot({
                   y0 <- y_in()
                   phaseR::flowField(goodwin,
                                      xlim = c(0,0.6), 
                                      ylim = c(0, 1.3), 
                                      parameters = c(input$sigmag, input$alphag, input$betag, input$gammag, input$rhog),
                                      points = 30, 
                                      add = FALSE,
                                      xlab = "a",
                                      ylab = "b")
                   phaseR::nullclines(goodwin,
                                      xlim = c(-1,3), 
                                      ylim = c(-1, 3),
                                      parameters = c(input$sigmag, input$alphag, input$betag, input$gammag, input$rhog), 
                                      points = 500)
                   phaseR::trajectory(goodwin, 
                                      y0 = y0, 
                                      tlim = c(0,input$tg),
                                      parameters = c(input$sigmag, input$alphag, input$betag, input$gammag, input$rhog), 
                                      colour = rep("black", 3))})))
conditionalPanel("input.model == 'Ramsey'",
                 absolutePanel(
                   width="100%", height = "100%",
                   renderPlot({
                     print(input)
                     ramsey.flowField <- phaseR::flowField(ramsey,
                                                           xlim = c(0.01,input$kr),
                                                           ylim = c(0.01,input$cr),
                                                           parameters = c(0.2,0.03,0.1,0.3),
                                                           points = 10,
                                                           add=F)
                     grid()
                     ramsey.nullclines <- phaseR::nullclines(
                       ramsey,
                       xlim = c(0,input$kr),
                       ylim = c(0.01,input$cr),
                       state.names = c('k','c'),
                       parameters = c(0.2,0.03,0.1,0.3),
                       points = 500,
                       col = c("blue","red"),
                       add.legend=T)})
                 ))
```



PhaseR and Our Tool{data-navmenu='About this Project' data-icon="ion-cube"} 
========================================================================

Link and short presentation of the package and the paper associated. 

Future Perspectives{data-navmenu='About this Project' data-icon='ion-ios-paperplane-outline'} 
========================================================================

Possibility of a package, extending/generalizing the tool to all macro 1-ODE and 2-ODE...

Resources{data-navmenu='Models' data-icon='ion-merge'}
========================================================================

In that page we can propose short econ/math developments on the models and/or links to the papers and teaching courses
