---
title: "FamiliaR with Dynamics"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    source_code: embed
    theme: spacelab
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(datasets)
library(ggplot2)
options(shiny.maxRequestSize = 30*1024^2)
data(faithful)
Solow1 <- function(s,k,a){
  y <- s*k^a
  return <- y
}
Solow2 <- function(d,k){
  y <- d*k+k^-1
}
solow_de <- function(t,y,parameters){
  s <- parameters[1]
  a <- parameters[2]
  del <- parameters[3]
  #k <- parameters[4]
  rhs <- s*y^a
  lhs <- del*y+(1/y)
  dy = rhs-lhs
  list(dy)
}

goodwin2<-function(t, state, parameters) {
  with(as.list(c(state, parameters)),{
    dV <- (a-b*U)*V
    dU <- (-c+d*V)*U
    dQ <- ((1-U)/sigma)*Q
    list(c(dV, dU, dQ))})}
    
goodwin <- function(t, y, parameters) {
  x <- y[1]
  y <- y[2]
  sigma <- parameters[1]
  alpha <- parameters[2]
  beta <- parameters[3]
  gamma <- parameters[4]
  rho <- parameters[5]
  A <- 1/sigma - alpha - beta
  B <- 1/sigma
  C <- gamma+alpha
  D <- rho
  dy <- numeric(2)
  dy[1] <- A*x - B*x*y
  dy[2] <- C*x*y - D*y
  list(dy)
}

ramsey <- function(t, y, parameters) {
  x <- y[1] #capital dc/dt
  y <- y[2] #consumption dk/dt
  theta <- parameters[1]
  rho <- parameters[2]
  delta <- parameters[3]
  alpha <- parameters[4]
  dy <- numeric(2)
  r <- alpha*x^(alpha-1)
  dy[1] <- x^alpha-y-delta*x
  dy[2] <- (y*(r-theta-delta))/delta
  list(dy)
}

shone <- function(t, y, parameters){
  ry <- y[1] # real output
  pie <- y[2] # expected inflation
  c0 <- parameters[1]
  i0 <- parameters[2]
  G <- parameters[3]
  b <- parameters[4]
  k <- parameters[5]
  d <- parameters[6]
  h <- parameters[7]
  tau <- parameters[8]
  alpha <- parameters[9]
  beta <- parameters[10]
  mdot <- parameters[11]
  yn <- parameters[12]
  a0 <- (c0+i0+G)/(1-b*(1-tau)+((h*k)/d))
  a1 <- (h/d)/(1-b*(1-tau)+((h*k)/d))
  a2 <- h/(1-b*(1-tau)+((h*k)/d))
  dy <- numeric(2)
  dy[1] <- a1*mdot-alpha*(a1-a2*beta)*(ry-yn)-a1*pie
  dy[2] <- beta*alpha*(y-yn)
  list(dy)
}
```

Dynamics {data-navmenu='Models' data-icon='ion-levels'}
=======================================================================

Column {.sidebar}
-----------------------------------------------------------------------

Select your model and the value of each parameters.

```{r}
selectInput("model", label = "Economic Model:",
            choices = c("Solow", "Ramsey", "OLG", "Goodwin"), selected = "Solow")
conditionalPanel("input.model == 'Solow'",
                 sliderInput("k", label = "Chart length (k):", min = 1, max = 100, value = 20, step = 1),
                 sliderInput("s", label = "Saving rate:", min = 0, max = 1, value =0.2, step = 0.01),
                 sliderInput("a", label = "Elasticty:", min = 0, max = 1, value =0.3, step = 0.01),
                 sliderInput("d", label = "Depreciation:", min = 0, max = 1, value =0.02, step = 0.01),
                 sliderInput("n", label = "Population growth rate:", min = 0, max = 1, value =0.5, step = 0.01),
                 sliderInput("t", label = "Time", min = 0, max = 100, value =20, step = 5),
                 numericInput('k0', 'Initial capital, k0:', 3, min=0.5, max=200),
                 actionButton("go","(Re)start Numeric Simulation")
)

conditionalPanel("input.model == 'Ramsey'",
                 sliderInput("t", label = "Time", min = 0, max = 200, value = 50, step = 5),
                 sliderInput("c", label = "Consumption, dc/dt",min = 0, max = 5, value = 3, step = 0.05),
                 sliderInput("k", label = "Capital, dk/dt", min = 0, max = 50, value = 30, step = 0.5),
                 sliderInput("theta", label = "Elasticity, tendendy of consumers to smooth their consumption over time:", min = 0, max = 1, value = 0.03, step = 0.01),
                 sliderInput("rho", label = "Rate at which consumers discount their future consumption", min = 0, max = 1, value = 0.2, step = 0.01),
                 sliderInput("delta", label = "Depreciation rate of capital", min = 0, max = 1, value = 0.1, step = 0.01),
                 sliderInput("alpha", label = "Elasticity parameter (measuring the responsiveness of the output production to changes in the input capital):", min = 0, max = 1, value = 0.3, step = 0.01),
                 
)        

```

Column
-----------------------------------------------------------------------

### Numerical Simulations

```{r}
renderPlot({
  if (input$model == "Solow")  {
    req(input$go)
    phaseR::flowField(solow_de,
              xlim   = c(0.0001, input$t),
              ylim   = c(0.0001, input$k),
              parameters = c(input$s,input$a,input$d),
              points=10,
              system = 'one.dim',
              add = F,
              xlab = 't',
              ylab = 'dk/dt')
    
    phaseR::nullclines(solow_de,
                      xlim   = c(0.0001, input$t),
                      ylim <- c(0.0001,input$k),
                      parameters = c(input$s,input$a,input$d),
                      system = "one.dim",
                      state.names = 'k')
    
    phaseR::trajectory(solow_de, 
                  y0 = input$k0, 
                  tlim = c(0,500),
                  parameters = c(input$s,input$a,input$d), 
                  system = "one.dim", 
                  colour = rep("black"),
                  add = T)
  }
  else if (input$model == "Goodwin")  {
    parameters <- c(a = 1.5,
                b = 1.8,
                c = 0.8,
                d = 0.8,
                sigma=0.8)
    state <- c(V = 0.5,
           U = 1,
           Q = 1)
    times <- seq(0, 20, by = 0.01)
    out <- deSolve::ode(y = state, times = times, func = goodwin2, parms = parameters)
    par(oma = c(0, 0, 3, 0))
    plot(out, xlab = "time", ylab = "-")
  }
  
  else if (input$model == "Ramsey"){
    ramsey.numericalSolution <- phaseR::numericalSolution(
    ramsey,
    y0 = c(0.5,0.1),
    tlim = c(0,20),
    tstep = 0.01,
    add.grid = T,
    type = "one",
    parameters = c(0.2,0.03,0.1,0.3),
    colour = c("green","orange"),
    ylab = "x,y",
    xlab = "t",
    ylim = c(0,5)
)
    
  }
    
})
```


Column {.tabset}
-----------------------------------------------------------------------

### Dynamics

```{r}
#renderPrint(input$model)
#uiOutput("dynamic")
renderPlot({
  k <- 1:input$k
  if (input$model == "Solow")  {
    ggplot()+
      geom_line(aes(x = k, y = Solow1(input$s,k, input$a), color = "blue"))+
      geom_line(aes(x=k,y=Solow2(input$d, k), color = "red"))+
      theme_bw()
    #plot(k,Solow(input$s,k, input$a), type="l")
    #lines(k,Solow(input$s,k, -input$a), type="l")
    }
})
```

### Phase Portrait/Phase Diagram

```{r}
renderPlot({
  if (input$model == "Solow") {
    phaseR::phasePortrait(solow_de,
                      ylim <- c(0.5,input$k),
                      parameters = c(input$s,input$a,input$d),
                      col = 'black',
                      add.grid = T,
                      xlab='k',
                      ylab='dk/dt')
  }
  else if (input$model == "Goodwin") {
    phaseR::flowField(goodwin, 
                                     xlim = c(0,1.5), 
                                     ylim = c(0, 1.5), 
                                     parameters = c(0.25, 0.6, 0.2, 0.3, 0.4), 
                                     points = 19, 
                                     add = FALSE)
    phaseR::nullclines(goodwin, 
                                       xlim = c(0,1.5), 
                                       ylim = c(0, 1.5),
                                       parameters = c(0.25, 0.6, 0.2, 0.3, 0.4), 
                                       points = 500)
  y0 <- matrix(c(0.2, 1, 0.6, 1, 1.1, 1), ncol = 2, nrow = 3, byrow = TRUE)
  phaseR::trajectory(goodwin, 
                                       y0 = y0, 
                                       tlim = c(0,10),
                                       parameters = c(0.25, 0.6, 0.2, 0.3, 0.4), 
                                       colour = rep("black", 3))
  }
  else if (input$model == "Ramsey") {
    ramsey.flowField <- phaseR::flowField(
    ramsey,
    xlim = c(0.01,input$k),
    ylim = c(0.01,input$c),
    parameters = c(0.2,0.03,0.1,0.3),
                 points = 10,
                 add=F
)
    grid()
    
    ramsey.nullclines <- phaseR::nullclines(
    ramsey,
    xlim = c(0,input$k),
    ylim = c(0.01,input$c),
    state.names = c('k','c'),
    parameters = c(0.2,0.03,0.1,0.3),
    points = 500,
    col = c("blue","red"),
    add.legend=T
)
  }
})
```



PhaseR and Our Tool{data-navmenu='About this Project' data-icon="ion-cube"} 
========================================================================

Link and short presentation of the package and the paper associated. 

Future Perspectives{data-navmenu='About this Project' data-icon='ion-ios-paperplane-outline'} 
========================================================================

Possibility of a package, extending/generalizing the tool to all macro 1-ODE and 2-ODE...

Resources{data-navmenu='Models' data-icon='ion-merge'}
========================================================================

In that page we can propose short econ/math developments on the models and/or links to the papers and teaching courses
